\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.5 in,top=0.5in,right=0.5 in,bottom=0.5in]{geometry} % Slightly tighter margins
\name{Sergei Kleimenov} 
\address{+31-6-44758718 \\ The Netherlands} 
\address{\href{mailto:sergeykleymenov@gmail.com}{sergeykleymenov@gmail.com} \\ 
\href{https://www.linkedin.com/in/sergei-kleimenov-13937419/}{https://www.linkedin.com/in/sergei-kleimenov-13937419/} \\ 
\href{https://t.me/skleymenov}{t.me/skleymenov}}  

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\begin{rSection}{Objective}
Senior Site Reliability Engineer / Tech Lead with 15+ years in designing and scaling distributed systems. 
Expert in Kubernetes, Docker, Terraform, AWS, GCP, Go, Python, and Linux. 
Proven success in improving service availability, automating infrastructure, and leading cross-functional teams. 
Seeking to drive reliability and scalability for large-scale platforms in the Netherlands.
\end{rSection}

%----------------------------------------------------------------------------------------
%	KEY SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Key Skills}
Kubernetes \textbullet{} Docker \textbullet{} Terraform \textbullet{} AWS \textbullet{} GCP \textbullet{} Nebius Cloud \textbullet{} Go \textbullet{} Python \textbullet{} Linux \textbullet{} CI/CD \textbullet{} Prometheus \textbullet{} Grafana \textbullet{} Site Reliability Engineering \textbullet{} Cloud Architecture \textbullet{} Team Leadership \textbullet{} AI/LLM
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\textbf{Team Leader} \hfill Aug 2024 -- Oct 2025 \\
Nebius B.V. \hfill Amsterdam, The Netherlands
\begin{itemize}
  \item Led multi-region expansion of 3 managed services, sustaining 99.95\% uptime.
  \item Engineered proof of concept for a new managed service.
  \item Enhanced Kubernetes service and optimized CI/CD pipelines, reducing deployment time.
\end{itemize}

\textbf{CTO / Technical Fellow \& Co-founder} \hfill Jan 2024 -- May 2025 \\
Rollyy Oy \hfill Hybrid/Remote, Finland
\begin{itemize}
  \item Co-founded and led startup developing autonomous charging robots.
\end{itemize}

\textbf{Project Manager / Team Lead} \hfill Mar 2021 -- Mar 2023 \\
SberAutoTech \hfill Moscow, Russia
\begin{itemize}
  \item Directed architecture and MVP delivery of autonomous driving systems.
  \item Built and led a 12-engineer team developing backend and SRE services.
\end{itemize}

\textbf{Site Reliability Engineer / DevOps Engineer} \hfill Jan 2016 -- Jun 2020 \\
Yandex \hfill Moscow, Russia
\begin{itemize}
  \item Conducted design reviews for core cloud runtime components serving 1M+ users.
  \item Built CI/CD, logging, and monitoring systems for self-driving car division.
  \item On-call engineer for 24/7 operation of critical resource management and monitoring.
\end{itemize}

\textbf{Earlier Experience} \hfill 2005 -- 2016
\begin{itemize}
  \item T-Platforms: Chief Integration Specialist, Head of QA, HPC Specialist – led deployments of large HPC clusters (LRZ Germany, CSC Finland, JRC Germany) and contributed to MSU “Lomonosov” supercomputer (\#12 in Top500 at launch).
  \item A.N. Bach Institute: Software Developer – Linux drivers, databases, GUI/TUI clients, mathematical libraries.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
M.V. Lomonosov Moscow State University \hfill 2002 -- 2008 \\
Department of Physics, Coursework completed \hfill Moscow, Russia
\end{rSection}

\end{document}
