\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sergei Kleimenov} 

\address{+31-6-44758718 \\ The Netherlands} 
\address{\href{mailto:sergeykleymenov@gmail.com}{sergeykleymenov@gmail.com} \\ \href{https://www.linkedin.com/in/sergey-kleymenov-13937419/}{https://www.linkedin.com/in/sergey-kleymenov-13937419/} \\ \href{https://t.me/skleymenov}{https://t.me/skleymenov}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Senior Site Reliability Engineer / Tech Lead with 15+ years of experience designing and scaling reliable distributed systems. 
Expert in Kubernetes, Go, and cloud platforms (AWS/GCP), skilled in Terraform, Prometheus, Grafana, CI/CD pipelines with proven success improving service availability, automating infrastructure with Terraform, and leading cross-functional teams. Seeking to apply deep SRE and leadership expertise to build resilient, large-scale platforms in the Netherlands.}

\end{rSection}

%----------------------------------------------------------------------------------------
%	KEY SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Key Skills}
\center
Kubernetes \textbullet{}
Docker \textbullet{}
Terraform \textbullet{}
AWS \textbullet{}
GCP \textbullet{}
Nebius Cloud \textbullet{}
Go \textbullet{}
Python \textbullet{}
Linux \textbullet{}
CI/CD \textbullet{}
Prometheus \\
Grafana \textbullet{}
Site Reliability Engineering \textbullet{}
Cloud Architecture \textbullet{}
Team Leadership \textbullet{}
LLM \textbullet{}
AI
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Team Leader} \hfill Aug 2024 - Oct 2025\\
Nebius B.V. \hfill \textit{Amsterdam, The Netherlands}
\begin{itemize}
	\itemsep -3pt {}
	\item Led multi-region expansion of 3 managed services, maintaining 99.95\% uptime.
	\item Engineered a proof of concept for a new managed service.
	\item Developed a TeamCity plug-in integrating AI-driven automation.
	\item Enhanced the managed Kubernetes service, improving stability and user experience.
	\item Optimized CI/CD pipelines, reducing deployment time and increasing automation efficiency.
\end{itemize}

\textbf{CTO / Technical Fellow \& co-founder} \hfill Jan 2024 - May 2025\\
Rollyy Oy \hfill \textit{hybrid/remote Finland}
\begin{itemize}
	\item Co-founded and led early-stage startup developing autonomous charging robots.
\end{itemize}

\textbf{Project Manager} \hfill Mar 2021 - Mar 2022\\
SberAutoTech \hfill \textit{Moscow, Russia}
\begin{itemize}
   \itemsep -3pt {}
   \item Served as Technical Leader, Project Manager and product owner in the field of autonomous driving systems from scratch to MVP.
   \item Supervised Hardware and Software architecture of Autonomous articulated lorry project.

\end{itemize}

\textbf{Team Leader} \hfill Jul 2020 - Mar 2021\\
SberAutoTech \hfill \textit{Moscow, Russia}
\begin{itemize}
   \itemsep -3pt {}
   \item Gathered the team of 12 Python developers and SREs.
   \item Built domain architecture.
   \item Developed a number of backend services.
\end{itemize}

\textbf{DevOps engineer and Team Leader} \hfill Sep 2017 - Jun 2020\\
Yandex \hfill \textit{Moscow, Russia}
\begin{itemize}
   \itemsep -3pt {}
   \item Contributed to the development of a continuous delivery system, logging and configuration management systems for the self-driving cars project.
   \item Gathered the support team for test drivers and QA engineers.
   \item Participated in developing software and business processes of the fleet management.
\end{itemize}

\pagebreak

\textbf{Site Reliability Engineer} \hfill Jan 2016 - Aug 2017\\
Yandex \hfill \textit{Moscow, Russia}
\begin{itemize}
   \itemsep -3pt {}
   \item Conducted design reviews for core runtime cloud components, ensuring scalability to support 1M+ daily users.
   \item Served as on-call engineer responsible for 24/7 operations of the resource management, cloud monitoring and configuration management systems.
\end{itemize}

\textbf{Chief Integration and Implementation Specialist} \hfill Nov 2012 - Jan 2016\\
T-Platforms \hfill \textit{Moscow, Russia and Hanover, Germany}
\begin{itemize}
   \itemsep -3pt {}
   \item Led installations of new HPC systems at 5+ customer sites.
   \item Developed cluster management and deployment software.
   \item Served as chief architect and technical leader of HPC projects in LRZ (Germany), CSC (Finland), JRC (Germany).
\end{itemize}

\textbf{Head of HW Quality} \hfill Aug 2010 - Oct 2012\\
T-Platforms \hfill \textit{Moscow, Russia}
\begin{itemize}
   \itemsep -3pt {}
   \item Led hardware/software QA team of 4 engineers.
   \item Participated in the development of business processes, ensuring they aligned with industry best practices.
   \item Developed automated functional and load testing software to be used on multiple production sites in China.
\end{itemize}

\textbf{HPC Specialist} \hfill Nov 2008 - Dec 2010\\
T-Platforms \hfill \textit{Moscow, Russia}
 \begin{itemize}
    \itemsep -3pt {}
    \item Led 20+ pre-sales projects as the chief architect. Consulted business development managers, as well as customers' technical and management staff.
    \item Designed 15+ HPC systems, ranging from single servers to multi-hundred TFlops clusters.
    \item Deployed HPC systems on variety of sites of different customers, including government organizations without Internet access. Served as 3rd level of support as well as remote HPC system administrator.
    \item Contributed to projects like the supercomputer "Lomonosov" at MSU (\#12 at the moment of installation in Top500). Was responsible for first deployment of T-Blade II product.
 \end{itemize}

\textbf{Software Developer} \hfill Jul 2005 - Apr 2008\\
A.N.Bach Institute of Biochemistry of RAS \hfill \textit{Moscow, Russia}
 \begin{itemize}
    \itemsep -3pt {}
    \item Developed Linux device drivers for a number of data acquisition devices (USB, PCI).
    \item Developed client-server system with custom application level multicast protocol.
    \item Developed GUI ( Qt3 and Java) and TUI client applications.
    \item Developed SQL database (mySQL and firebird) as the backend for data storage.
    \item Implemented XML document export scripts and printable report generation scripts based on bash, latex, XSLT.
    \item Contributed to the development of a new data approximation algorithm, which utilized cubic B-splines. This involved creating a set of Matlab functions and a Linux shared library written in C.
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

M.V. Lomonosov Moscow State University \hfill {2002 - 2008}\\
Department of Physics, Coursework completed \hfill \textit{Moscow, Russia}

\end{rSection}
\end{document}
